---
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(kableExtra)
library(fontawesome)
library(readr)
library(dplyr)
library(tidyr)

process.frame <- function(data.frame) {
  # data.frame <- data.frame[order(data.frame$end, na.last = FALSE, decreasing = TRUE), ]
  data.frame <- data.frame %>% arrange(aspect, !is.na(end), end, award)
  data.frame$start <- as.character(data.frame$start)
  data.frame$end <- as.character(data.frame$end)
  data.frame$end <- data.frame$end %>% replace_na("Present")
  data.frame$date <- if_else(data.frame$start != data.frame$end,
                             paste(data.frame$start, "-", data.frame$end),
                             data.frame$start)
  data.frame <- data.frame %>% select(-start, -end)
}

target.year <- "2019 - Present"
```
<style>
  body {
    font-family: "Georgia Pro";
    font-size: 12pt;
    color: #191919;
    }
  .myTable td {
    padding: 0.25em;
    font-family: "Georgia Pro";
    vertical-align: top;
  }
  .straightTable {
    padding-left: 1.75em;
  }
  .straightTable td {
    padding: 0.25em;
    font-family: "Georgia Pro";
    vertical-align: top;
  }
  h2 {
    color: #990000;
    font-size: 1em;
    font-family: "BentonSans";
    font-weight: bold;
    text-align: left;
    text-transform: uppercase;
    text-decoration: underline;
  }
  h2::after {
    content: ":";
  }
  h3 {
    color: #990000;
    font-size: 1em;
    font-family: "BentonSans";
    font-weight: bold;
    text-align: left;
    text-transform: uppercase;
  }
  h3::after {
    content: ":";
  }
  .heading {
    font-family: "BentonSansCond";
    width: 100%;
    text-align: center;
    margin: 0px auto;
    padding-top: 0.25em;
    overflow: auto;
    font-size: 10pt;
    text-transform: uppercase;
  }
.heading h1 {
    font-family: BentonSans;
    font-weight: bold;
    font-size: 2em;
  }
  .heading a {
    color: #191919;
    font-family: 'JetBrains Mono NL';
    font-size: 9pt;
  }
</style>

<div class="heading">

<h1> Jeremy Forest Price, PhD </h1>

Urban Teacher Education | IU School of Education-Indianapolis at IUPUI<br />
ES 3162 | 902 West New York Street | Indianapolis, IN 46206<br />
<a href="mailto:jfprice@iupui.edu">jfprice@iupui.edu</a> | 1.317.274.6808

</div>


## Education

```{r education}
source("education.R")

education.table <- kbl(education.frame, col.names = NULL, label = NULL, table.attr='class="myTable"') %>%
  pack_rows("Graduate", 1, 3, label_row_css = "border-bottom: 0 px; text-transform: uppercase; font-family: BentonSans;") %>%
  pack_rows("Undergraduate", 4, 4, label_row_css = "border-bottom: 0 px; text-transform: uppercase; font-family: BentonSans;") %>%
  kable_minimal(full_width = TRUE) %>%
  column_spec(1:2, width = "42%") %>%
  column_spec(3, width = "14%")

education.table
```

## Appointments

```{r appointments}
source("appointments.R")

appointments.table <- kbl(appointments.frame, col.names = NULL, label = NULL, table.attr='class="myTable"', align = "llr") %>%
  pack_rows("Academic", 1, 3, label_row_css = "border-bottom: 0 px; text-transform: uppercase; font-family: BentonSans;") %>%
  pack_rows("Non-Academic", 4, 5, label_row_css = "border-bottom: 0 px; text-transform: uppercase; font-family: BentonSans;") %>%
  kable_minimal(full_width = TRUE) %>%
  column_spec(1:2, width = "42%") %>%
  column_spec(3, width = "14%")

appointments.table
```

## Professional Memberships

  * blah blah blah
  * blah blah blah
  * blah blah blah

## Awards and Honors

```{r awards, warning = FALSE, message = FALSE}

  awards.frame <- read_csv(file = "awards.csv", col_names = TRUE) %>%
  process.frame()
  


  awards.count <- awards.frame %>% count(aspect)
  awards.count <- as.data.frame(t(awards.count))
  colnames(awards.count) <- awards.count[1,]
  awards.count <- awards.count[-1,]
  awards.count$service <- ifelse(("service" %in% colnames(awards.count)) == FALSE, 0, awards.count$service)
  awards.count <- awards.count %>% select(teaching, research, service)
  teach.end <- as.numeric(awards.count$teaching)
  research.start <- as.numeric(awards.count$teaching) + 1
  research.end <- as.numeric(awards.count$research) + as.numeric(awards.count$research)

awards.frame$aspect <- as.factor(awards.frame$aspect)
awards.frame$aspect <- relevel(awards.frame$aspect, "teaching")
awards.frame <- awards.frame %>% arrange(desc(aspect), desc(date), award)
awards.frame <- awards.frame %>% select(-aspect)
  
awards.table <- kbl(awards.frame, col.names = NULL, label = NULL, table.attr='class="myTable"', align = "llr") %>%
  pack_rows("Teaching", 1, teach.end, label_row_css = "border-bottom: 0 px; text-transform: uppercase; font-family: BentonSans;") %>%
  pack_rows("Research and Scholarship", research.start, research.end, label_row_css = "border-bottom: 0 px; text-transform: uppercase; font-family: BentonSans;") %>%
  kable_minimal(full_width = TRUE) %>%
  column_spec(1:2, width = "42%") %>%
  column_spec(3, width = "14%") %>%
  row_spec(which(awards.frame$date == target.year), bold = FALSE, background = "#FDF7E7")

awards.table
```

## Professional Development
  * blah
  * blah
  * blah
  
## Teaching

### Teaching Assignments
  * blah
  * blah
  * blah

### Mentoring

### Teaching Administration and Curriculum Development

### Grants/Fellowships in Teaching

### Invited Presentations---Teaching

## Research/Creative Activity

### Grants/Fellowships in Research
  * blah
  * blah
  * blah
  
### Invited Presentations---Research

## Service and Leadership

### University Leadership and Service

### Professional and Community Leadership and Service

### Grants/Fellowships in Leadership and Service

## Publications

### Teaching

### Research

### Leadership and Service

## Media Coverage
