---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(kableExtra)
library(fontawesome)
library(readr)
library(dplyr)
library(tidyr)

process.frame <- function(data.frame) {
  # data.frame <- data.frame[order(data.frame$end, na.last = FALSE, decreasing = TRUE), ]
  data.frame <- data.frame %>% arrange(!is.na(end), end, award)
  data.frame$start <- as.character(data.frame$start)
  data.frame$end <- as.character(data.frame$end)
  data.frame$end <- data.frame$end %>% replace_na("Present")
  data.frame$date <- if_else(data.frame$start != data.frame$end,
                             paste(data.frame$start, "-", data.frame$end),
                             data.frame$start)
  data.frame <- data.frame %>% select(-start, -end)
}
```

<style>
  body {
    font-family: Spectral;
    font-size: 12pt;
    color: #191919;
    }
  .myTable td {
    padding: 0.25em;
    font-family: Spectral;
    vertical-align: top;
  }
  .straightTable {
    padding-left: 1.75em;
  }
  .straightTable td {
    padding: 0.25em;
    font-family: Spectral;
    vertical-align: top;
  }
  h2 {
    color: #990000;
    font-size: 11pt;
    font-family: "Public Sans";
    font-weight: normal;
    text-align: right;
  }
  .content {
    width: 100%;
    margin: 0px auto;
    padding-top: 0.25em;
    overflow: auto;
  }
   .content .leftcol {
    float: left;
    width: 15%;
  }
  .content .rightcol {
    float: right;
    width: 85%;
    padding-top: 0.6em;
  }
  .heading {
    width: 100%;
    margin: 0px auto;
    padding-top: 0.25em;
    overflow: auto;
    font-size: 10pt;
    border-bottom: solid 2px #990000;
  }
h1 {
    font-size: 3em;
    text-align: right;
  }
  .heading .leftcol {
    float: left;
    width: 65%;
    text-align: right;
  }
  .heading .rightcol {
    float: right;
    width: 35%;
    text-align: right;
  }
  .heading a {
    color: #191919;
    font-family: 'JetBrains Mono NL';
    font-size: 9pt;
  }
</style>

<div class="heading">

<h1> Jeremy Forest Price, PhD </h1>

<div class="leftcol">
  Department of Urban Teacher Education<br />
  IU School of Education-Indianapolis at IUPUI<br />
  902 West New York Street<br />
  Indianapolis, IN 46206
</div>
<div class="rightcol">
  1.317.274.6808 `r fa("phone", fill = "#990000")` <br />
  <a href="mailto:jfprice@iupui.edu">jfprice@iupui.edu</a> `r fa("envelope", fill = "#990000")` <br />
  <a href="">dr_jfprice</a> `r fa("twitter", fill = "#990000")` <br />
  <a href="">jfprice</a> `r fa("github-alt", fill = "#990000")` 
</div>
</div>

<div class="content">
<div class="leftcol">
  <h2>education</h2>
</div>

<div class="rightcol">
```{r education, warning = FALSE}
source("education.R")
education.table <- kbl(education.frame, col.names = NULL, label = NULL, table.attr='class="myTable"') %>%
  pack_rows("Graduate", 1, 3, label_row_css = "border-bottom: 0 px; font-style: italic;") %>%
  pack_rows("Undergraduate", 4, 4, label_row_css = "border-bottom: 0 px; font-style: italic; padding-top: 0.5em;") %>%
  kable_minimal(full_width = TRUE) %>%
  column_spec(1:2, width = "42%") %>%
  column_spec(3, width = "14%")
education.table
```
</div>
</div>

<div class="content">
<div class="leftcol">
  <h2>appointments</h2>
</div>

<div class="rightcol">
```{r appointments, warning = FALSE}
source("appointments.R")
appointments.table <- kbl(appointments.frame, col.names = NULL, label = NULL, table.attr='class="myTable"', align = "llr") %>%
  pack_rows("Academic", 1, 3, label_row_css = "border-bottom: 0 px; font-style: italic;") %>%
  pack_rows("Non-Academic", 4, 5, label_row_css = "border-bottom: 0 px; font-style: italic; padding-top: 0.5em;") %>%
  kable_minimal(full_width = TRUE) %>%
  column_spec(1:2, width = "42%") %>%
  column_spec(3, width = "14%")
appointments.table
```
</div>
</div>

<div class="content">
<div class="leftcol">
  <h2>awards and honors</h2>
</div>

<div class="rightcol">
```{r awards, warning = FALSE, message = FALSE}
awards.frame <- read_csv(file = "awards.csv", col_names = TRUE) %>%
  select(-aspect) %>%
  process.frame()

awards.table <- kbl(awards.frame, col.names = NULL, label = NULL, table.attr='class="straightTable"', align = "llr") %>%
  kable_minimal(full_width = TRUE) %>%
  column_spec(1:2, width = "41%") %>%
  column_spec(3, width = "18%")
awards.table
```
</div>
</div>